---
title: "Text Mining Notes"
author: "Susan Hajmohammad"
date: "February 25, 2019"
output: html_document
---


```{r setup, include=FALSE}

library(dplyr)
library(gutenbergr)
library(tm)
library(tidytext)
library(stringr)
library(tidyr)
library(topicmodels)
library(ggplot2)
library(tidytext)


```








 
```{r, include=FALSE}

##Regular expressions


#castle_otranto <- gutenberg_download(696)

#frankenstein <- gutenberg_download(41445)

#the_vampyre <- gutenberg_download(6087)

#old_english_baron <- gutenberg_download(5182)

#mysteries_udolpho <- gutenberg_download(3268)


# books <- gutenberg_download(c(696, 41445, 6087, 5182, 3268), meta_fields = "title")
# 
# 
# books %>% 
#   count(title)


#gothic_books <- gutenberg_metadata %>%
  #filter(gutenberg_subjects == "Gothic fiction")


```
 
 
 
 
 
 
```{r, include=FALSE}





gothic_books <- gutenberg_subjects%>%
  filter(subject == "Gothic fiction (Literary genre)")


# gb <- gutenberg_metadata %>%
#   gutenberg_subjects(subject == "Gothic fiction (Literary genre)")%>%
#   gutenberg_download(meta_fields = "author")

gf <- gutenberg_metadata%>%
  filter(gutenberg_bookshelf == "Gothic Fiction")


gb <- gutenberg_metadata


goth <- str_detect(gb, "gothic")





# authors <- gutenberg_metadata %>%
#   count(author, sort = TRUE, meta_fields )
#   
# 
# 
# gothic_authors <- authors %>%
#   filter(gutenberg_bookshelf == "Gothic fiction",
#          language == "en",
#          !str_detect(title, "Works"),
#          has_text,
#          !str_detect(rights, "Copyright")) %>%
#          distinct(title)




#gothic_books_1 <- gutenberg_subjects%>%
  #filter(gutenberg_bookshelf == "Gothic fiction")


gothic_df <- gutenberg_download(gothic_books)


# gothic_df <- gutenberg_metadata%>%
#   gutenberg_download(meta_fields = "author")
#   gutenberg_download(gothic_books)

summary(gothic_df)


#gothic_df%>% 
  #group_by(gutenberg_bookshelf)


#detective <- gutenberg_subjects %>%
  #filter(subject == "Detective and mystery stories")



subjects <- gutenberg_subjects


```


```{r }



# words <- books %>%
#   unnest_tokens(word, text)
# 
# 
# word_counts <- words %>%
#   anti_join(stop_words, by = "word") %>%
#   count(title, word, sort = TRUE)%>%
#   group_by(title)
# 
# word_counts


```



```{r }

gutenberg_metadata




horace <- gutenberg_works(author == "Walpole, Horace")

#gutenberg_authors%>%
  #filter(author == "HORACE WALPOLE")



```



Notes: 
  
  **Gutenbergr Vinnette** 
   
  For basics like title, author and language
    
  Use "gutenberg_metadata"
      
  ex: library(dplyr)

  gutenberg_metadata %>%
      filter(title == "Wuthering Heights")
    
  gutenberg_works(author == "Austen, Jane")
    
  "pre-filters" the data set 
      
      
*Another way to filter*      
      library(stringr)
gutenberg_works(str_detect(author, "Austen"))


*To download a book using the ID you can use*

  wuthering_heights <- gutenberg_download(768)
  wuthering_heights


You can find book IDs on ???


*How to filter by subjects*

gutenberg_subjects %>%
  filter(subject == "Detective and mystery stories")

  
*To find info on the authors* 

gutenberg_authors()



  
  **Units of Analysis**
  
 *This is to make a dataframe of all the words*
 
  library(tidytext)

words <- books %>%
  unnest_tokens(word, text)

words


*This counts the amount of times each word is used*

word_counts <- words %>%
  anti_join(stop_words, by = "word") %>%
  count(title, word, sort = TRUE)

word_counts




    










Works Cited:

Gutenbergr<https://cran.r-project.org/web/packages/gutenbergr/index.html>
Gutenbergr <https://cran.r-project.org/web/packages/gutenbergr/vignettes/intro.html>
tm:Text Mining Package<https://cran.r-project.org/web/packages/tm/index.html>
tm <https://cran.r-project.org/web/packages/tm/vignettes/tm.pdf>
Gutenber.org <https://www.gutenberg.org/ebooks/subject/2586?start_index=51>
Info on gothic lit via WIKI <https://en.wikipedia.org/wiki/Gothic_fiction#Early_Gothic_romances>
Gutenbergr <https://cran.r-project.org/web/packages/gutenbergr/README.html>
String functions <https://rdrr.io/r/>
Gutenbergr <https://ropensci.org/tutorials/gutenbergr_tutorial/>
Gutenbergr pdf <https://cran.r-project.org/web/packages/gutenbergr/gutenbergr.pdf>
Text mining with Tidy Verse <https://books.google.com/books?hl=en&lr=&id=qNcnDwAAQBAJ&oi=fnd&pg=PP1&dq=gutenbergr+text+mining&ots=Q0zQ8pMXu2&sig=8Kd4-5TuF2JY6S3Gf8KhfhcSsIw#v=onepage&q=gutenbergr%20text%20mining&f=false>
Text mining pdf <http://epub.wu.ac.at/3978/1/textmining.pdf>
<https://cran.r-project.org/web/packages/tidytext/vignettes/topic_modeling.html>
<>
<>
<>
<>
<>
<>






